Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-16 automatica/paper.tex
fixes

\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck} \note{Num\_States = ?, plant\_typet = ? controller_typet =?}, checks that the candidate
solution $K$, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.  After unfolding the transition system corresponding
to the previously synthesized controller $k$ steps, we check that the safety
specification holds for any initial state.

@@

\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus
operation performed on the last bit. 
Thus, $\delta_T$ is the truncation error and it will propagate across
operations.
%
\item {\bf Rounding:} The following errors appear in basic operations.  Let
$c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
the truncation errors caused by representing $c_1$ and $c_2$ in the
fixed-point domain as above.
%
\begin{enumerate}
%
\item Addition/Subtraction: these operations only propagate errors coming
from truncation of the operands, namely $\mathcal{F}_{\langle I,F
\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
%
\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
$c_m=2^{-F}$ as above.
%
\item Division: the operations performed by our controllers in the FWL
domain do not include division.  However, we do use division in computations
at the precision of the plant.  Here the error depends on whether the
divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
%
%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
\end{enumerate}

\item {\bf Overflow:}
The maximum size of a real number $x$ that can be represented in a fixed
point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
the domain.  We check that overflow does not occur.

>>>>

\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck} \note{$Num\_States = ?, plant\_typet = ? controller_typet =?$}, checks that the candidate
solution $K$, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.  After unfolding the transition system corresponding
to the previously synthesized controller $k$ steps, we check that the safety
specification holds for any initial state.

@@

\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
error $ \delta_T=x\ \%_{c_m}\ \tilde x$ \note{define tilde x}, and $\%_{c_m}$ is the modulus
operation performed on the last bit. 
Thus, $\delta_T$ is the truncation error and it will propagate across
operations.
%
\item {\bf Rounding:} The following errors are due to basic arithmetic operations.  
Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
the truncation errors caused by representing $c_1$ and $c_2$ in a fixed-point domain.
%
\begin{enumerate}
%
\item Addition/Subtraction: these operations only propagate errors coming
from truncation of the operands, namely $\mathcal{F}_{\langle I,F
\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
%
\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
$c_m=2^{-F}$ as above.
%
\item Division: the operations performed by the controllers in the FWL
domain do not include division.  However, we do use division in computations within the plant.  
Here the error depends on whether the divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$, 
where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
%
%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
\end{enumerate}

\item {\bf Overflow:}
The maximum size of a real number $x$ that can be represented in a fixed
point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
the domain.  We check that overflow does not occur \note{and if it does \ldots}.
